Report

### 2021-05-07 report.Rmd
Late update + add range of temporal data in stations

```{r}
loadd(predict_plot2)
pred_plot_signif_com <- predict_plot2 %>%
  filter(
    y %in% c(get_com_str_var(), "log_rich_std", "piel_nind", "piel_bm"),
    !y %in% c("bm_std", "rich_std"),
    x == "log_bm_std"
  )
legend_signif <- get_legend(
  pred_plot_signif_com$pred_plot[[1]] +
    theme(legend.position = "bottom")
)
pred_plot_signif_com %<>% 
  mutate(
  pred_plot = pmap(list(pred_plot, y, x),
    function(p, y, x) {
      # Replace label
      label <- str_replace_all(c(x,y), var_replacement(slope = TRUE)) 
      p +
	labs(x = label[1], y = label[2]) +
	theme(legend.position = "none")
    } )
  )

list_p <- pred_plot_signif_com$pred_plot
list_p[[length(list_p) + 1]] <- legend_signif

pred_plot1 <- plot_grid(
  plotlist = list_p,
  labels = "AUTO",
  nrow = 2
)
#pred_plot1 <- plot_grid(top, legend_signif, nrow = 2, rel_heights = c(1, .1))
```

```{r}
pred_plot_rich <- predict_plot2 %>%
  filter( y %in% c(get_com_str_var(), "log_bm_std", "piel_nind", "piel_bm"), x == "log_rich_std") %>%
  filter(!y %in% c("rich_std"))
legend_signif <- get_legend(
  pred_plot_rich$pred_plot[[1]] +
    theme(legend.position = "bottom")
)
pred_plot_rich %<>% 
  mutate(
  pred_plot = pmap(list(pred_plot, y, x),
    function(p, y, x) {
      # Replace label
      label <- str_replace_all(c(x,y), var_replacement(slope = TRUE)) 
      p +
	labs(x = label[1], y = label[2]) +
	theme(legend.position = "none")
    } )
  )

list_p <- pred_plot_rich$pred_plot
list_p[[length(list_p) + 1]] <- legend_signif

pred_plot2 <- plot_grid(
  plotlist = list_p,
  nrow = 2,
  labels = "AUTO" 
)
#pred_plot2 <- plot_grid(top, legend_signif, nrow = 2, rel_heights = c(1, .1))
```

```{r}

pred_plot_other <- predict_plot2 %>%
  filter( y %in% c("ct_ff", "w_trph_lvl_avg"), x %in% c("ct_ff", "w_trph_lvl_avg"))
legend_signif <- get_legend(
  pred_plot_other$pred_plot[[1]] +
    theme(legend.position = "bottom")
)
pred_plot_other %<>% 
  mutate(
  pred_plot = pmap(list(pred_plot, y, x),
    function(p, y, x) {
      # Replace label
      label <- str_replace_all(c(x,y), var_replacement(slope = TRUE)) 
      p +
	labs(x = label[1], y = label[2]) +
	theme(legend.position = "none")
    } )
  )

list_p <- pred_plot_other$pred_plot
list_p[[length(list_p) + 1]] <- legend_signif

pred_plot3 <- plot_grid(
  plotlist = list_p,
  labels = "AUTO", nrow = 2
)
#pred_plot3 <- plot_grid(top, legend_signif, nrow = 2, rel_heights = c(1, .1))
```

```{r, fig.dim = c(10, 7)}
pred_plot1
pred_plot2
pred_plot3
```

```{r, eval = FALSE, fig.dim = c(12, 12)}
plot_grid(
  , plot_grid(, , ncol = 2, rel_widths = c(.75, 1)),
  nrow = 2
)
```

@@

summary_var_f3y %>%
  na.omit() %>%
  select(bm_std, avg_IS, l, ld, m, A, gini, log_bm_std, connectance, ct_ff, rich_std, w_trph_lvl_avg,
    weighted_connectance, nbnode_std, nb_pisc_node_std, prop_pisc_node, piel_bm,
    piel_nind) %>%
  cor() %>%
  corrplot::corrplot(corr = .)
```

@@

```{r pred-other-com, fig.dim = c(12, 10)}
pred_plot_signif <- predict_plot2 %>%
  filter(!y %in% c(get_com_str_var(), "ct_ff"), x == "log_bm_std")
legend_signif2 <- get_legend(
  pred_plot_signif_com$pred_plot[[1]] + theme(legend.position = "bottom")
)
pred_plot_signif$pred_plot %<>% map(., ~.x + theme(legend.position = "none"))
top2 <- plot_grid(
  plotlist = pred_plot_signif$pred_plot,
  labels = pred_plot_signif$y
)
plot_grid(top2, legend_signif2, nrow = 2, rel_heights = c(1, .1))
```

@@

>>>>

```{r}
loadd(p_fig1_2)
loadd(predict_plot2)
pl <- get_plot_fig1_2(predict_plot2, get_list = TRUE)

map(pl$bm, function (plo) {
  plo + theme(legend.position = "none")

  save_plot(
    file = get_mypath(
      "figures", 
      paste0(str_replace_all(plo$labels$y, " ", "_"),
	"_",
	str_replace_all(plo$labels$x, " ", "_"),
	".png"
      )
      ),
    plot = plo,
    base_height = 4, base_asp = 1.2#1.618 
  )

} 
)
map(pl$rich, function (plo) {

  plo + theme(legend.position = "none")

  save_plot(
    file = get_mypath(
      "figures", 
      paste0(str_replace_all(plo$labels$y, " ", "_"),
	"_",
	str_replace_all(plo$labels$x, " ", "_"),
	".png"
      )
      ),
    plot = plo,
    base_height = 4, base_asp = 1.2#1.618 
  )

} 
)

map(pl$nind, function (plo) {

  plo + theme(legend.position = "none")

  save_plot(
    file = get_mypath(
      "figures", 
      paste0(str_replace_all(plo$labels$y, " ", "_"),
	"_",
	str_replace_all(plo$labels$x, " ", "_"),
	".png"
      )
      ),
    plot = plo,
    base_height = 4, base_asp = 1.2#1.618 
  )

} 
)

pred_plot1 <- p_fig1_2[["bm"]]
pred_plot2 <- p_fig1_2[["rich"]]
pred_plot3 <- p_fig1_2[["other"]]
pred_plot4 <- p_fig1_2[["nind"]]
```

```{r, fig.dim = c(10, 7)}
pred_plot1
pred_plot2
pred_plot3
pred_plot4
```

@@

summary_var_f3y %>%
  na.omit() %>%
  select(bm_std, nind_std, log_bm_std, connectance, ct_ff, rich_std, w_trph_lvl_avg,
    weighted_connectance, nbnode_std, nb_pisc_node_std, prop_pisc_node, piel_bm,
    piel_nind) %>%
  cor() %>%
  corrplot::corrplot(corr = .)
```

@@

#### Réseau ~ Biomasse

```{r pred-other-com, fig.dim = c(12, 10)}
pred_plot_signif <- predict_plot2 %>%
  filter(!y %in% c(get_com_str_var(), "ct_ff"), x == "log_bm_std")
legend_signif2 <- get_legend(
  pred_plot_signif$pred_plot[[1]] + theme(legend.position = "bottom")
)
pred_plot_signif$pred_plot %<>% map(., ~.x + theme(legend.position = "none"))
top2 <- plot_grid(
  plotlist = pred_plot_signif$pred_plot,
  labels = pred_plot_signif$y
)
plot_grid(top2, legend_signif2, nrow = 2, rel_heights = c(1, .1))
```

@@

#### Réseau ~ richnes

```{r pred-other-com-rich, fig.dim = c(12, 10)}
pred_plot_signif <- predict_plot2 %>%
  filter(!y %in% c(get_com_str_var(), "ct_ff"), x == "log_rich_std")
legend_signif2 <- get_legend(
  pred_plot_signif$pred_plot[[1]] + theme(legend.position = "bottom")
)
pred_plot_signif$pred_plot %<>% map(., ~.x + theme(legend.position = "none"))
top2 <- plot_grid(
  plotlist = pred_plot_signif$pred_plot,
  labels = pred_plot_signif$y
)
plot_grid(top2, legend_signif2, nrow = 2, rel_heights = c(1, .1))
```

```{r}
model_log_rich_f3y_table_medium[["anova_table"]] %>% 
  filter(!y %in% get_com_str_var(all = FALSE)) %>%
  kable(., booktabs = TRUE,
    caption = 
      paste0(
      "ANOVA table for the model: dN =",
      "dB + B + dB*B + Inc*B + dB*Inc*B."
    )
  ) %>%
  kable_styling(latex_options =c("scale_down", "stripped")) %>%
  collapse_rows(columns = 1, valign = "top")
```
```{r}
```
